(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-26 ms.tex
SDSS data...

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers, as individuals
Brendan P. Bowler,
Andrew W. Mann,
David W. Latham,
% The observers, as a group
And Whoever DaveL Tells Us to Add as TRES Team Members
}

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey 
\citep[SDSS DR9,][]{Ahn12}. For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.

>>>>

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers, as PIs 
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Andrew W. Mann,
% The observers, as a group
And Whoever DaveL Tells Us to Add as TRES Team Members
}

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey 
\citep[SDSS DR9,][]{Ahn12}. 
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ Campaign 1 is 
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table 
\ref{Table:BGstars}.

%Table:BGstars
% Primary    RA Dec Separation DeltaR         MaxDepth
% 201295312  &  &   &          & 7.10 \pm 0.10 & 0.75
% 201465501  &  &   &          & 7.90 \pm 0.25 & 0.36
% 201546283  &  &   &          & 5.87 \pm 0.06 & 2.31
% 201779067  &  &   &          & 4.21 \pm 0.03 & 10.56

In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness...
